---
title: "Exploratory Analyasis"
author: "Wu Yiyang"
date: "2023-12-02"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(tidyverse)
library(readr)
library(ggplot2)
library(corrplot)
library(dplyr)
```



```{r}
raw_digital_proxy <- read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/US_SG_dataset.csv")
cleaned_data4<-read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/cleaned_data4.csv")
cleaned_data5<-read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/cleaned_data5.csv")
cleaned_data6<-read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/cleaned_data6.csv")
Help_Physical_care<-read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/Help_Physical_care.csv")
Help_Medical_care<- read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/Help_Medical_care.csv")
High_Stake<- read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/High_Stake.csv")
Low_Stake<- read_csv("~/OneDrive - University of Toronto/Digital Proxy Practicum/data/Low_Stake.csv")
```



# Distribution
# Demographics


```{r}
filterCountryData <- function(xyz) { # create a function with the name my_function
  test<-raw_digital_proxy%>%
    filter(Country==xyz)%>%
  return(test)
}
digital_proxyUS <- filterCountryData("US")
digital_proxySG <- filterCountryData("SG")

# view(digital_proxyUS)
```


```{r}
obs_dpUS <- nrow(digital_proxyUS)
var_dpUS <- ncol(digital_proxyUS)
print(obs_dpUS)
print(var_dpUS)

obs_dpSG <- nrow(digital_proxySG)
var_dpSG <- ncol(digital_proxySG)
print(obs_dpSG)
print(var_dpSG)
```


```{r}
#digital_proxyUS <- digital_proxyUS %>%select(Country, everything())

#digital_proxySG <- digital_proxySG %>%select(Country, everything())
```



## Age (Uniform Distribution)
```{r}
par(mfrow = c(2, 2))
Age<-as.numeric(digital_proxyUS$Age)

# histogram of the age variable
drawHistogram <- function(data,mainTitle,xlabel) { # create a function with the name my_function
  hist(data, main = mainTitle, xlab = xlabel)
}
drawHistogram(digital_proxyUS$Age,"Age distributionUS","Age")
drawHistogram(digital_proxySG$Age,"Age distributionSG","Age")

# density plot of the age variable
drawDensity<- function(data,mainTitle,xlabel) { # create a function with the name my_function
    plot(density(data), main = mainTitle, xlab = xlabel)
}
drawDensity(digital_proxyUS$Age,"Age distributionUS","Age")
drawDensity(digital_proxySG$Age,"Age distributionSG","Age")


# boxplot
drawboxplot <- function(data,mainTitle,xlabel) { # create a function with the name my_function
  boxplot(data, main = mainTitle, xlab = xlabel)
}
drawboxplot(digital_proxyUS$Age,"Age distributionUS","Age")
drawboxplot(digital_proxySG$Age,"Age distributionSG","Age")


# QQ plot (whether normal)
drawQQplot <- function(data,mainTitle,xlabel) { # create a function with the name my_function
  qqnorm(data, main = mainTitle, xlab = xlabel)
  qqline(data)
}
drawQQplot(digital_proxyUS$Age,"Age distributionUS","Age")
drawQQplot(digital_proxySG$Age,"Age distributionSG","Age")


#summary age
summarize <- function(data) {
  summary_stats <- c(
    Mean = mean(data),
    Median = median(data),
    Min = min(data),
    Max = max(data),
    Var = var(data),
    SD = sd(data)
  )
  return(summary_stats)
}
summarize(digital_proxyUS$Age)
summarize(digital_proxySG$Age)
```



```{r}
library(e1071)

# Assuming you have a numerical variable in a dataset called 'data'
skew <- skewness(digital_proxyUS$Age)
kurt <- kurtosis(digital_proxyUS$Age)
```


## Housing(Multinomial Distribution)

```{r}
summary(digital_proxyUS$Housing)

par(mfrow = c(1, 2))
Housing<-as.factor(digital_proxyUS$Housing)


# number of occurance
printtable <- function(data) { # create a function with the name my_function
  table(data)
}
printtable(digital_proxyUS$Housing)
printtable(digital_proxySG$Housing)


# barplot
drawbarplot <- function(data,mainTitle,xlabel) { # create a function with the name my_function
  barplot(table(data), main = mainTitle, xlab = xlabel)
}
drawbarplot(digital_proxyUS$Housing,"Bar Plot of Housing US","Housing")
drawbarplot(digital_proxySG$Housing,"Bar Plot of Housing SG","Housing")


# pie chart
drawpieplot <- function(data,mainTitle,xlabel) { # create a function with the name my_function
  pie(table(data), main = mainTitle, xlab = xlabel)
}
drawpieplot(digital_proxyUS$Housing,"Pie Chart of Housing US","Housing")
drawpieplot(digital_proxySG$Housing,"Pie Chart of Housing SG","Housing")


# percentage of each categories
percentagehousing <- function(data) { # create a function with the name my_function
  prop.table(table(data))
}
percentagehousing(digital_proxyUS$Housing)
percentagehousing(digital_proxySG$Housing)


```



## Income(Multinomial Distribution)

```{r}
summary(digital_proxyUS$Income)

par(mfrow = c(1, 2))
Income<-as.factor(digital_proxyUS$Income)

# number of occurance
printtable(digital_proxyUS$Income)
printtable(digital_proxySG$Income)

# barplot
drawbarplot(digital_proxyUS$Income,"Bar Plot of Income US","Income")
drawbarplot(digital_proxySG$Income,"Bar Plot of Income SG","Income")

# pie chart
drawpieplot(digital_proxyUS$Income,"Pie Chart of Income US","Income")
drawpieplot(digital_proxySG$Income,"Pie Chart of Income SG","Income")

# percentage of each categories
percentagehousing(digital_proxyUS$Income)
percentagehousing(digital_proxySG$Income)


```



## Gender(Bernoulli Distribution)

```{r}
summary(digital_proxyUS$Gender)

par(mfrow = c(1, 2))
Gender<-as.factor(digital_proxyUS$Gender)

# number of occurance
printtable(digital_proxyUS$Gender)
printtable(digital_proxySG$Gender)

# barplot
drawbarplot(digital_proxyUS$Gender,"Bar Plot of Gender US","Gender")
drawbarplot(digital_proxySG$Gender,"Bar Plot of Gender SG","Gender")

# pie chart
drawpieplot(digital_proxyUS$Gender,"Pie Chart of Gender US","Gender")
drawpieplot(digital_proxySG$Gender,"Pie Chart of Gender SG","Gender")

# percentage of each categories
percentagehousing(digital_proxyUS$Gender)
percentagehousing(digital_proxySG$Gender)


```


## Marital(Multinomial Distribution)

```{r}
summary(digital_proxyUS$Marital)

par(mfrow = c(1,2))
Marital<-as.factor(digital_proxyUS$Marital)

# number of occurance
printtable(digital_proxyUS$Marital)
printtable(digital_proxySG$Marital)

# barplot
drawbarplot(digital_proxyUS$Marital,"Bar Plot of Marital US","Marital")
drawbarplot(digital_proxySG$Marital,"Bar Plot of Marital SG","Marital")

# pie chart
drawpieplot(digital_proxyUS$Marital,"Pie Chart of Marital US","Marital")
drawpieplot(digital_proxySG$Marital,"Pie Chart of Marital SG","Marital")

# percentage of each categories
percentagehousing(digital_proxyUS$Marital)
percentagehousing(digital_proxySG$Marital)

```


## Ethnicity(Multinomial Distribution)

```{r}

summary(digital_proxyUS$Ethnicity)

par(mfrow = c(1,2))
Ethnicity<-as.factor(digital_proxyUS$Ethnicity)

# number of occurance
printtable(digital_proxyUS$Ethnicity)
printtable(digital_proxySG$Ethnicity)

# barplot
drawbarplot(digital_proxyUS$Ethnicity,"Bar Plot of Ethnicity US","Ethnicity")
drawbarplot(digital_proxySG$Ethnicity,"Bar Plot of Ethnicity SG","Ethnicity")

# pie chart
drawpieplot(digital_proxyUS$Ethnicity,"Pie Chart of Ethnicity US","Ethnicity")
drawpieplot(digital_proxySG$Ethnicity,"Pie Chart of Ethnicity SG","Ethnicity")

# percentage of each categories
percentagehousing(digital_proxyUS$Ethnicity)
percentagehousing(digital_proxySG$Ethnicity)

unique(digital_proxyUS$EthnicityOthers)


```



## Religion(Multinomial Distribution)

```{r}
summary(digital_proxyUS$Religion_New)

par(mfrow = c(1,2))
Religion_New<-as.factor(digital_proxyUS$Religion_New)

# number of occurance
printtable(digital_proxyUS$Religion_New)
printtable(digital_proxySG$Religion_New)

# barplot
drawbarplot(digital_proxyUS$Religion_New,"Bar Plot of Religion US","Religion")
drawbarplot(digital_proxySG$Religion_New,"Bar Plot of Religion SG","Religion")

# pie chart
drawpieplot(digital_proxyUS$Religion_New,"Pie Chart of Religion US","Religion")
drawpieplot(digital_proxySG$Religion_New,"Pie Chart of Religion SG","Religion")

# percentage of each categories
percentagehousing(digital_proxyUS$Religion_New)
percentagehousing(digital_proxySG$Religion_New)


```


## Education(Multinomial Distribution)

```{r}
summary(digital_proxyUS$Education)

par(mfrow = c(1,2))
Education<-as.factor(digital_proxyUS$Education)


# number of occurance
printtable(digital_proxyUS$Education)
printtable(digital_proxySG$Education)

# barplot
drawbarplot(digital_proxyUS$Education,"Bar Plot of Education US","Education")
drawbarplot(digital_proxySG$Education,"Bar Plot of Education SG","Education")

# pie chart
drawpieplot(digital_proxyUS$Education,"Pie Chart of Education US","Education")
drawpieplot(digital_proxySG$Education,"Pie Chart of Education SG","Education")

# percentage of each categories
percentagehousing(digital_proxyUS$Education)
percentagehousing(digital_proxySG$Education)


```


## Employment(Multinomial Distribution)

```{r}
summary(digital_proxyUS$Employment)

par(mfrow = c(1,2))
Employment<-as.factor(digital_proxyUS$Employment)

# number of occurance
printtable(digital_proxyUS$Employment)
printtable(digital_proxySG$Employment)

# barplot
drawbarplot(digital_proxyUS$Employment,"Bar Plot of Employment US","Employment")
drawbarplot(digital_proxySG$Employment,"Bar Plot of Employment SG","Employment")

# pie chart
drawpieplot(digital_proxyUS$Employment,"Pie Chart of Employment US","Employment")
drawpieplot(digital_proxySG$Employment,"Pie Chart of Employment SG","Employment")

# percentage of each categories
percentagehousing(digital_proxyUS$Employment)
percentagehousing(digital_proxySG$Employment)



```


## Citizen (Bernoulli Distribution)

```{r}
summary(digital_proxyUS$Citizen)

par(mfrow = c(1,2))
Citizen<-as.factor(digital_proxyUS$Citizen)


# number of occurance
printtable(digital_proxyUS$Citizen)
printtable(digital_proxySG$Citizen)

# barplot
drawbarplot(digital_proxyUS$Citizen,"Bar Plot of Citizen US","Citizen")
drawbarplot(digital_proxySG$Citizen,"Bar Plot of Citizen SG","Citizen")

# pie chart
drawpieplot(digital_proxyUS$Citizen,"Pie Chart of Citizen US","Citizen")
drawpieplot(digital_proxySG$Citizen,"Pie Chart of Citizen SG","Citizen")

# percentage of each categories
percentagehousing(digital_proxyUS$Citizen)
percentagehousing(digital_proxySG$Citizen)


```


## Siblings(Exponential Distribution)

```{r}

# histogram of the Siblings variable
drawHistogram(digital_proxyUS$Siblings,"Siblings distributionUS","Siblings")
drawHistogram(digital_proxySG$Siblings,"Siblings distributionSG","Siblings")

# density plot of the Siblings variable
drawDensity(digital_proxyUS$Siblings,"Siblings distributionUS","Siblings")
drawDensity(digital_proxySG$Siblings,"Siblings distributionSG","Siblings")

# boxplot
drawboxplot(digital_proxyUS$Siblings,"Siblings distributionUS","Siblings")
drawboxplot(digital_proxySG$Siblings,"Siblings distributionSG","Siblings")

# QQ plot (whether normal)
drawQQplot(digital_proxyUS$Siblings,"Siblings distributionUS","Siblings")
drawQQplot(digital_proxySG$Siblings,"Siblings distributionSG","Siblings")


#summary Siblings
summarize(digital_proxyUS$Siblings)
summarize(digital_proxySG$Siblings)

```



## SiblingsOrder(Multinomial Distribution)

```{r}
summary(digital_proxyUS$SiblingsOrder)

par(mfrow = c(1,2))
SiblingsOrder<-as.factor(digital_proxyUS$SiblingsOrder)

# number of occurance
printtable(digital_proxyUS$SiblingsOrder)
printtable(digital_proxySG$SiblingsOrder)

# barplot
drawbarplot(digital_proxyUS$SiblingsOrder,"Bar Plot of SiblingsOrder US","SiblingsOrder")
drawbarplot(digital_proxySG$SiblingsOrder,"Bar Plot of SiblingsOrder SG","SiblingsOrder")

# pie chart
drawpieplot(digital_proxyUS$SiblingsOrder,"Pie Chart of SiblingsOrder US","SiblingsOrder")
drawpieplot(digital_proxySG$SiblingsOrder,"Pie Chart of SiblingsOrder SG","SiblingsOrder")

# percentage of each categories
percentagehousing(digital_proxyUS$SiblingsOrder)
percentagehousing(digital_proxySG$SiblingsOrder)

```



# Physical Care Tasks

## HelpFam, HelpRel, HelpFre (Poisson Distribution)

```{r}
summary(digital_proxyUS$HelpImmediateFam)
summary(digital_proxyUS$HelpRelatives)
summary(digital_proxyUS$HelpFriends)

HelpImmediateFam<-as.factor(digital_proxyUS$HelpImmediateFam)
HelpRelatives<-as.factor(digital_proxyUS$HelpRelatives)
HelpFriends<-as.factor(digital_proxyUS$HelpFriends)


# number of occurance
printtable(digital_proxyUS$HelpImmediateFam)
printtable(digital_proxySG$HelpImmediateFam)
printtable(digital_proxyUS$HelpRelatives)
printtable(digital_proxySG$HelpRelatives)
printtable(digital_proxyUS$HelpFriends)
printtable(digital_proxySG$HelpFriends)

# barplot
drawbarplot(digital_proxyUS$HelpImmediateFam,"Bar Plot of HelpImmediateFam US","HelpImmediateFam")
drawbarplot(digital_proxySG$HelpImmediateFam,"Bar Plot of HelpImmediateFam SG","HelpImmediateFam")
drawbarplot(digital_proxyUS$HelpRelatives,"Bar Plot of HelpRelatives US","HelpRelatives")
drawbarplot(digital_proxySG$HelpRelatives,"Bar Plot of HelpRelatives SG","HelpRelatives")
drawbarplot(digital_proxyUS$HelpFriends,"Bar Plot of HelpFriends US","HelpFriends")
drawbarplot(digital_proxySG$HelpFriends,"Bar Plot of HelpFriends SG","HelpFriends")


# percentage of each categories
percentagehousing(digital_proxyUS$HelpImmediateFam)
percentagehousing(digital_proxySG$HelpImmediateFam)
percentagehousing(digital_proxyUS$HelpRelatives)
percentagehousing(digital_proxySG$HelpRelatives)
percentagehousing(digital_proxyUS$HelpFriends)
percentagehousing(digital_proxySG$HelpFriends)



```


## HelpOthers_new, HelpOthsnum, HelpPassAway (Poisson Distribution)

```{r}
# HelpOthers_new
# summary(digital_proxyUS$HelpOthers_new)
# summary(digital_proxyUS$HelpOthersNum)
# summary(digital_proxyUS$HelpPassAway)

HelpOthers<-as.factor(digital_proxyUS$HelpOthers_new)


# number of occurance
printtable(digital_proxyUS$HelpOthers_new)
printtable(digital_proxySG$HelpOthers_new)
printtable(digital_proxyUS$HelpOthersNum)
printtable(digital_proxySG$HelpOthersNum)
printtable(digital_proxyUS$HelpPassAway)
printtable(digital_proxySG$HelpPassAway)

# barplot
drawbarplot(digital_proxyUS$HelpOthers_new,"Bar Plot of HelpOthers_new US","HelpOthers_new")
drawbarplot(digital_proxySG$HelpOthers_new,"Bar Plot of HelpOthers_new SG","HelpOthers_new")
drawbarplot(digital_proxyUS$HelpOthersNum,"Bar Plot of HelpOthersNum US","HelpOthersNum")
drawbarplot(digital_proxySG$HelpOthersNum,"Bar Plot of HelpOthersNum SG","HelpOthersNum")
drawbarplot(digital_proxyUS$HelpPassAway,"Bar Plot of HelpPassAway US","HelpPassAway")
drawbarplot(digital_proxySG$HelpPassAway,"Bar Plot of HelpPassAway SG","HelpPassAway")


# percentage of each categories
percentagehousing(digital_proxyUS$HelpOthers_new)
percentagehousing(digital_proxySG$HelpOthers_new)
percentagehousing(digital_proxyUS$HelpOthersNum)
percentagehousing(digital_proxySG$HelpOthersNum)
percentagehousing(digital_proxyUS$HelpPassAway)
percentagehousing(digital_proxySG$HelpPassAway)

```


```{r}
# unique(digital_proxyUS$HelpOthers_new)
new_data_frame_US <- digital_proxyUS[, c("HelpImmediateFam","HelpRelatives","HelpFriends","HelpWork","HelpIrrelevant","HelpOthers_new")]
head(new_data_frame_US)

new_data_frame_SG <- digital_proxySG[, c("HelpImmediateFam","HelpRelatives","HelpFriends","HelpWork","HelpIrrelevant","HelpOthers_new")]
head(new_data_frame_SG)
```


## HelpFood(Multinomial Distribution)

```{r}
summary(digital_proxyUS$HelpFood)

par(mfrow = c(1,2))
HelpFood<-as.factor(digital_proxyUS$HelpFood)

# number of occurance
printtable(digital_proxyUS$HelpFood)
printtable(digital_proxySG$HelpFood)

# barplot
drawbarplot(digital_proxyUS$HelpFood,"Bar Plot of HelpFood US","HelpFood")
drawbarplot(digital_proxySG$HelpFood,"Bar Plot of HelpFood SG","HelpFood")

# pie chart
drawpieplot(digital_proxyUS$HelpFood,"Pie Chart of HelpFood US","HelpFood")
drawpieplot(digital_proxySG$HelpFood,"Pie Chart of HelpFood SG","HelpFood")

# percentage of each categories
percentagehousing(digital_proxyUS$HelpFood)
percentagehousing(digital_proxySG$HelpFood)

```


## HelpHousekeep(Multinomial Distribution)

```{r}
summary(digital_proxyUS$HelpHousekeep)

par(mfrow = c(1,2))
HelpHousekeep<-as.factor(digital_proxyUS$HelpHousekeep)

# number of occurance
printtable(digital_proxyUS$HelpHousekeep)
printtable(digital_proxySG$HelpHousekeep)

# barplot
drawbarplot(digital_proxyUS$HelpHousekeep,"Bar Plot of HelpHousekeep US","HelpHousekeep")
drawbarplot(digital_proxySG$HelpHousekeep,"Bar Plot of HelpHousekeep SG","HelpHousekeep")

# pie chart
drawpieplot(digital_proxyUS$HelpHousekeep,"Pie Chart of HelpHousekeep US","HelpHousekeep")
drawpieplot(digital_proxySG$HelpHousekeep,"Pie Chart of HelpHousekeep SG","HelpHousekeep")

# percentage of each categories
percentagehousing(digital_proxyUS$HelpHousekeep)
percentagehousing(digital_proxySG$HelpHousekeep)

```



## HelpLaundry(Multinomial Distribution)

```{r}
summary(digital_proxyUS$HelpLaundry)

par(mfrow = c(1,2))
HelpLaundry<-as.factor(digital_proxyUS$HelpLaundry)

# number of occurance
printtable(digital_proxyUS$HelpLaundry)
printtable(digital_proxySG$HelpLaundry)

# barplot
drawbarplot(digital_proxyUS$HelpLaundry,"Bar Plot of HelpLaundry US","HelpLaundry")
drawbarplot(digital_proxySG$HelpLaundry,"Bar Plot of HelpLaundry SG","HelpLaundry")

# pie chart
drawpieplot(digital_proxyUS$HelpLaundry,"Pie Chart of HelpLaundry US","HelpLaundry")
drawpieplot(digital_proxySG$HelpLaundry,"Pie Chart of HelpLaundry SG","HelpLaundry")

# percentage of each categories
percentagehousing(digital_proxyUS$HelpLaundry)
percentagehousing(digital_proxySG$HelpLaundry)


```



## HelpTransport(Multinomial Distribution)

```{r}
summary(digital_proxyUS$HelpTransport)

par(mfrow = c(1,2))
HelpTransport<-as.factor(digital_proxyUS$HelpTransport)

# number of occurance
printtable(digital_proxyUS$HelpTransport)
printtable(digital_proxySG$HelpTransport)

# barplot
drawbarplot(digital_proxyUS$HelpTransport,"Bar Plot of HelpTransport US","HelpTransport")
drawbarplot(digital_proxySG$HelpTransport,"Bar Plot of HelpTransport SG","HelpTransport")

# pie chart
drawpieplot(digital_proxyUS$HelpTransport,"Pie Chart of HelpTransport US","HelpTransport")
drawpieplot(digital_proxySG$HelpTransport,"Pie Chart of HelpTransport SG","HelpTransport")

# percentage of each categories
percentagehousing(digital_proxyUS$HelpTransport)
percentagehousing(digital_proxySG$HelpTransport)

```



## HelpMed(Multinomial Distribution)

```{r}
summary(digital_proxyUS$HelpMed)

par(mfrow = c(1,2))
HelpMed<-as.factor(digital_proxyUS$HelpMed)

# number of occurance
printtable(digital_proxyUS$HelpMed)
printtable(digital_proxySG$HelpMed)

# barplot
drawbarplot(digital_proxyUS$HelpMed,"Bar Plot of HelpMed US","HelpMed")
drawbarplot(digital_proxySG$HelpMed,"Bar Plot of HelpMed SG","HelpMed")

# pie chart
drawpieplot(digital_proxyUS$HelpMed,"Pie Chart of HelpMed US","HelpMed")
drawpieplot(digital_proxySG$HelpMed,"Pie Chart of HelpMed SG","HelpMed")

# percentage of each categories
percentagehousing(digital_proxyUS$HelpMed)
percentagehousing(digital_proxySG$HelpMed)

```



## HelpFinance(Multinomial Distribution)

```{r}
summary(digital_proxyUS$HelpFinance)

par(mfrow = c(1,2))
HelpFinance<-as.factor(digital_proxyUS$HelpFinance)

# number of occurance
printtable(digital_proxyUS$HelpFinance)
printtable(digital_proxySG$HelpFinance)

# barplot
drawbarplot(digital_proxyUS$HelpFinance,"Bar Plot of HelpFinance US","HelpFinance")
drawbarplot(digital_proxySG$HelpFinance,"Bar Plot of HelpFinance SG","HelpFinance")

# pie chart
drawpieplot(digital_proxyUS$HelpFinance,"Pie Chart of HelpFinance US","HelpFinance")
drawpieplot(digital_proxySG$HelpFinance,"Pie Chart of HelpFinance SG","HelpFinance")

# percentage of each categories
percentagehousing(digital_proxyUS$HelpFinance)
percentagehousing(digital_proxySG$HelpFinance)


```



## HelpDigital(Multinomial Distribution)

```{r}
summary(digital_proxyUS$HelpDigital)

par(mfrow = c(1,2))
HelpDigital<-as.factor(digital_proxyUS$HelpDigital)

# number of occurance
printtable(digital_proxyUS$HelpDigital)
printtable(digital_proxySG$HelpDigital)

# barplot
drawbarplot(digital_proxyUS$HelpDigital,"Bar Plot of HelpDigital US","HelpDigital")
drawbarplot(digital_proxySG$HelpDigital,"Bar Plot of HelpDigital SG","HelpDigital")

# pie chart
drawpieplot(digital_proxyUS$HelpDigital,"Pie Chart of HelpDigital US","HelpDigital")
drawpieplot(digital_proxySG$HelpDigital,"Pie Chart of HelpDigital SG","HelpDigital")

# percentage of each categories
percentagehousing(digital_proxyUS$HelpDigital)
percentagehousing(digital_proxySG$HelpDigital)

```




## ADL: Bath, Groom, Toilet, Transfer, Incontinence, Feed (Multinomial Distribution)

```{r}
digital_proxyUS_ADL<-digital_proxyUS%>%
  select(ADLBath, ADLGroom, ADLToilet, ADLTransfer, ADLIncontinence, ADLFeed)
digital_proxySG_ADL<-digital_proxySG%>%
  select(ADLBath, ADLGroom, ADLToilet, ADLTransfer, ADLIncontinence, ADLFeed)

# summary(digital_proxyUS_ADL$ADLBath)

par(mfrow = c(2,2))
ADLBath<-as.factor(digital_proxyUS_ADL$ADLBath)
ADLGroom<-as.factor(digital_proxyUS_ADL$ADLGroom)
ADLToilet<-as.factor(digital_proxyUS_ADL$ADLToilet)
ADLTransfer<-as.factor(digital_proxyUS_ADL$ADLTransfer)
ADLIncontinence<-as.factor(digital_proxyUS_ADL$ADLIncontinence)
ADLFeed<-as.factor(digital_proxyUS_ADL$ADLFeed)


# number of occurance
printtable(digital_proxyUS_ADL$ADLBath)
printtable(digital_proxySG_ADL$ADLBath)

printtable(digital_proxyUS_ADL$ADLGroom)
printtable(digital_proxySG_ADL$ADLGroom)

printtable(digital_proxyUS_ADL$ADLToilet)
printtable(digital_proxySG_ADL$ADLToilet)

printtable(digital_proxyUS_ADL$ADLTransfer)
printtable(digital_proxySG_ADL$ADLTransfer)

printtable(digital_proxyUS_ADL$ADLIncontinence)
printtable(digital_proxySG_ADL$ADLIncontinence)

printtable(digital_proxyUS_ADL$ADLFeed)
printtable(digital_proxySG_ADL$ADLFeed)

# barplot
drawbarplot(digital_proxyUS_ADL$ADLBath,"Bar Plot of ADLBath US","ADLBath")
drawbarplot(digital_proxySG_ADL$ADLBath,"Bar Plot of ADLBath SG","ADLBath")

drawbarplot(digital_proxyUS_ADL$ADLGroom,"Bar Plot of ADLGroom US","ADLGroom")
drawbarplot(digital_proxySG_ADL$ADLGroom,"Bar Plot of ADLGroom SG","ADLGroom")

drawbarplot(digital_proxyUS_ADL$ADLToilet,"Bar Plot of ADLToilet US","ADLToilet")
drawbarplot(digital_proxySG_ADL$ADLToilet,"Bar Plot of ADLToilet SG","ADLToilet")

drawbarplot(digital_proxyUS_ADL$ADLTransfer,"Bar Plot of ADLTransfer US","ADLTransfer")
drawbarplot(digital_proxySG_ADL$ADLTransfer,"Bar Plot of ADLTransfer SG","ADLTransfer")

drawbarplot(digital_proxyUS_ADL$ADLIncontinence,"Bar Plot of ADLIncontinence US","ADLIncontinence")
drawbarplot(digital_proxySG_ADL$ADLIncontinence,"Bar Plot of ADLIncontinence SG","ADLIncontinence")

drawbarplot(digital_proxyUS_ADL$ADLFeed,"Bar Plot of ADLFeed US","ADLFeed")
drawbarplot(digital_proxySG_ADL$ADLFeed,"Bar Plot of ADLFeed SG","ADLFeed")


# percentage of each categories
percentagehousing(digital_proxyUS_ADL$ADLBath)
percentagehousing(digital_proxySG_ADL$ADLBath)

percentagehousing(digital_proxyUS_ADL$ADLGroom)
percentagehousing(digital_proxySG_ADL$ADLGroom)

percentagehousing(digital_proxyUS_ADL$ADLToilet)
percentagehousing(digital_proxySG_ADL$ADLToilet)

percentagehousing(digital_proxyUS_ADL$ADLTransfer)
percentagehousing(digital_proxySG_ADL$ADLTransfer)

percentagehousing(digital_proxyUS_ADL$ADLIncontinence)
percentagehousing(digital_proxySG_ADL$ADLIncontinence)

percentagehousing(digital_proxyUS_ADL$ADLFeed)
percentagehousing(digital_proxySG_ADL$ADLFeed)

```




## Medical Delegation

## MedicalHelpImmediateFam, MedicalHelpRelatives, MedicalHelpFriends (Multinomial Distribution)

```{r}
#summary(digital_proxyUS$MedicalHelpImmediateFam)
#summary(digital_proxyUS$MedicalHelpRelatives)
#summary(digital_proxyUS$MedicalHelpFriends)

MedicalHelpImmediateFam<-as.factor(digital_proxyUS$MedicalHelpImmediateFam)
MedicalHelpRelatives<-as.factor(digital_proxyUS$MedicalHelpRelatives)
MedicalHelpFriends<-as.factor(digital_proxyUS$MedicalHelpFriends)

# number of occurance
printtable(digital_proxyUS$MedicalHelpImmediateFam)
printtable(digital_proxySG$MedicalHelpImmediateFam)
printtable(digital_proxyUS$MedicalHelpRelatives)
printtable(digital_proxySG$MedicalHelpRelatives)
printtable(digital_proxyUS$MedicalHelpFriends)
printtable(digital_proxySG$MedicalHelpFriends)

# barplot
drawbarplot(digital_proxyUS$MedicalHelpImmediateFam,"Bar Plot of MedicalHelpImmediateFam US","MedicalHelpImmediateFam")
drawbarplot(digital_proxySG$MedicalHelpImmediateFam,"Bar Plot of MedicalHelpImmediateFam SG","MedicalHelpImmediateFam")
drawbarplot(digital_proxyUS$MedicalHelpRelatives,"Bar Plot of MedicalHelpRelatives US","MedicalHelpRelatives")
drawbarplot(digital_proxySG$MedicalHelpRelatives,"Bar Plot of MedicalHelpRelatives SG","MedicalHelpRelatives")
drawbarplot(digital_proxyUS$MedicalHelpFriends,"Bar Plot of MedicalHelpFriends US","MedicalHelpFriends")
drawbarplot(digital_proxySG$MedicalHelpFriends,"Bar Plot of MedicalHelpFriends SG","MedicalHelpFriends")


# percentage of each categories
percentagehousing(digital_proxyUS$MedicalHelpImmediateFam)
percentagehousing(digital_proxySG$MedicalHelpImmediateFam)
percentagehousing(digital_proxyUS$MedicalHelpRelatives)
percentagehousing(digital_proxySG$MedicalHelpRelatives)
percentagehousing(digital_proxyUS$MedicalHelpFriends)
percentagehousing(digital_proxySG$MedicalHelpFriends)

```


## MedicalHelpOthers, MedicalHelpOthersNum, MedicalHelpPassAway (Poisson Distribution)

```{r}
summary(digital_proxyUS$MedicalHelpOthers_new)
summary(digital_proxyUS$MedicalHelpOthersNum)
summary(digital_proxyUS$MedicalHelpPassAway)

MedicalHelpOthers<-as.factor(digital_proxyUS$MedicalHelpOthers_new)
MedicalHelpOthersNum<-as.factor(digital_proxyUS$MedicalHelpOthersNum)
MedicalHelpPassAway<-as.factor(digital_proxyUS$MedicalHelpPassAway)


# number of occurance
printtable(digital_proxyUS$MedicalHelpOthers_new)
printtable(digital_proxySG$MedicalHelpOthers_new)
printtable(digital_proxyUS$MedicalHelpOthersNum)
printtable(digital_proxySG$MedicalHelpOthersNum)
printtable(digital_proxyUS$MedicalHelpPassAway)
printtable(digital_proxySG$MedicalHelpPassAway)

# barplot
drawbarplot(digital_proxyUS$MedicalHelpOthers_new,"Bar Plot of MedicalHelpOthers_new US","MedicalHelpOthers_new")
drawbarplot(digital_proxySG$MedicalHelpOthers_new,"Bar Plot of MedicalHelpOthers_new SG","MedicalHelpOthers_new")
drawbarplot(digital_proxyUS$MedicalHelpOthersNum,"Bar Plot of MedicalHelpOthersNum US","MedicalHelpOthersNum")
drawbarplot(digital_proxySG$MedicalHelpOthersNum,"Bar Plot of MedicalHelpOthersNum SG","MedicalHelpOthersNum")
drawbarplot(digital_proxyUS$MedicalHelpPassAway,"Bar Plot of MedicalHelpPassAway US","MedicalHelpPassAway")
drawbarplot(digital_proxySG$MedicalHelpPassAway,"Bar Plot of MedicalHelpPassAway SG","MedicalHelpPassAway")


# percentage of each categories
percentagehousing(digital_proxyUS$MedicalHelpOthers_new)
percentagehousing(digital_proxySG$MedicalHelpOthers_new)
percentagehousing(digital_proxyUS$MedicalHelpOthersNum)
percentagehousing(digital_proxySG$MedicalHelpOthersNum)
percentagehousing(digital_proxyUS$MedicalHelpPassAway)
percentagehousing(digital_proxySG$MedicalHelpPassAway)

```


```{r}
new_data_frame_medical_US <- digital_proxyUS[, c("MedicalHelpImmediateFam","MedicalHelpRelatives","MedicalHelpFriends","MedicalHelpWork","MedicalHelpIrrelevant","MedicalHelpOthers_new")]
head(new_data_frame_medical_US)

new_data_frame_medical_SG <- digital_proxySG[, c("MedicalHelpImmediateFam","MedicalHelpRelatives","MedicalHelpFriends","MedicalHelpWork","MedicalHelpIrrelevant","MedicalHelpOthers_new")]
head(new_data_frame_medical_SG)
```


## Medical Delegation Action (Low-Stake Activities):

## MedicalMakeAppt(Poisson Distribution)

```{r}

par(mfrow = c(1,2))
FinanceAction<-as.factor(digital_proxyUS$MedicalMakeAppt)


# number of occurance
printtable(digital_proxyUS$MedicalMakeAppt)
printtable(digital_proxySG$MedicalMakeAppt)

# barplot
drawbarplot(digital_proxyUS$MedicalMakeAppt,"Bar Plot of MedicalMakeAppt US","MedicalMakeAppt")
drawbarplot(digital_proxySG$MedicalMakeAppt,"Bar Plot of MedicalMakeAppt SG","MedicalMakeAppt")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalMakeAppt)
percentagehousing(digital_proxySG$MedicalMakeAppt)


```


## MedicalMakeApptFuture(Multinomial Distribution)

```{r}

# helpfoodfuture
digital_proxyUS_MedicalMakeApptFuture<-digital_proxyUS%>%
  select(MedicalMakeAppt,MedicalMakeApptFuture) %>%
  filter(MedicalMakeAppt=="Never")
digital_proxySG_MedicalMakeApptFuture<-digital_proxySG%>%
  select(MedicalMakeAppt,MedicalMakeApptFuture) %>%
  filter(MedicalMakeAppt=="Never")

par(mfrow = c(1,2))
MedicalMakeApptFuture<-as.factor(digital_proxyUS_MedicalMakeApptFuture$MedicalMakeApptFuture)
MedicalMakeApptFuture<-as.factor(digital_proxySG_MedicalMakeApptFuture$MedicalMakeApptFuture)

# number of occurance
printtable(digital_proxyUS_MedicalMakeApptFuture$MedicalMakeApptFuture)
printtable(digital_proxySG_MedicalMakeApptFuture$MedicalMakeApptFuture)

# barplot
drawbarplot(digital_proxyUS_MedicalMakeApptFuture$MedicalMakeApptFuture,"Bar Plot of MedicalMakeApptFuture US","MedicalMakeApptFuture")
drawbarplot(digital_proxySG_MedicalMakeApptFuture$MedicalMakeApptFuture,"Bar Plot of MedicalMakeApptFuture SG","MedicalMakeApptFuture")


# percentage of each categories
percentagehousing(digital_proxyUS_MedicalMakeApptFuture$MedicalMakeApptFuture)
percentagehousing(digital_proxySG_MedicalMakeApptFuture$MedicalMakeApptFuture)

```



## MedicalAccompanyAppt(Poisson Distribution)

```{r}
par(mfrow = c(1,2))
FinanceAction<-as.factor(digital_proxyUS$MedicalAccompanyAppt)


# number of occurance
printtable(digital_proxyUS$MedicalAccompanyAppt)
printtable(digital_proxySG$MedicalAccompanyAppt)

# barplot
drawbarplot(digital_proxyUS$MedicalAccompanyAppt,"Bar Plot of MedicalAccompanyAppt US","MedicalAccompanyAppt")
drawbarplot(digital_proxySG$MedicalAccompanyAppt,"Bar Plot of MedicalAccompanyAppt SG","MedicalAccompanyAppt")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalAccompanyAppt)
percentagehousing(digital_proxySG$MedicalAccompanyAppt)

```


## MedicalAccompanyApptFuture(Multinomial Distribution)

```{r}

# helpfoodfuture
digital_proxyUS_MedicalAccompanyApptFuture<-digital_proxyUS%>%
  select(MedicalAccompanyAppt,MedicalAccompanyApptFuture) %>%
  filter(MedicalAccompanyAppt=="Never")
digital_proxySG_MedicalAccompanyApptFuture<-digital_proxySG%>%
  select(MedicalAccompanyAppt,MedicalAccompanyApptFuture) %>%
  filter(MedicalAccompanyAppt=="Never")

par(mfrow = c(1,2))
MedicalAccompanyApptFuture<-as.factor(digital_proxyUS_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture)
MedicalAccompanyApptFuture<-as.factor(digital_proxySG_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture)

# number of occurance
printtable(digital_proxyUS_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture)
printtable(digital_proxySG_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture)

# barplot
drawbarplot(digital_proxyUS_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture,"Bar Plot of MedicalAccompanyApptFuture US","MedicalAccompanyApptFuture")
drawbarplot(digital_proxySG_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture,"Bar Plot of MedicalAccompanyApptFuture SG","MedicalAccompanyApptFuture")


# percentage of each categories
percentagehousing(digital_proxyUS_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture)
percentagehousing(digital_proxySG_MedicalAccompanyApptFuture$MedicalAccompanyApptFuture)

```



## MedicalTakeMeds(Poisson Distribution)

```{r}
par(mfrow = c(1,2))
FinanceAction<-as.factor(digital_proxyUS$MedicalTakeMeds)


# number of occurance
printtable(digital_proxyUS$MedicalTakeMeds)
printtable(digital_proxySG$MedicalTakeMeds)

# barplot
drawbarplot(digital_proxyUS$MedicalTakeMeds,"Bar Plot of MedicalTakeMeds US","MedicalTakeMeds")
drawbarplot(digital_proxySG$MedicalTakeMeds,"Bar Plot of MedicalTakeMeds SG","MedicalTakeMeds")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalTakeMeds)
percentagehousing(digital_proxySG$MedicalTakeMeds)

```


## MedicalTakeMedsFuture(Multinomial Distribution)

```{r}

# helpfoodfuture
digital_proxyUS_MedicalTakeMedsFuture<-digital_proxyUS%>%
  select(MedicalTakeMeds,MedicalTakeMedsFuture) %>%
  filter(MedicalTakeMeds=="Never")
digital_proxySG_MedicalTakeMedsFuture<-digital_proxySG%>%
  select(MedicalTakeMeds,MedicalTakeMedsFuture) %>%
  filter(MedicalTakeMeds=="Never")

par(mfrow = c(1,2))
MedicalTakeMedsFuture<-as.factor(digital_proxyUS_MedicalTakeMedsFuture$MedicalTakeMedsFuture)
MedicalTakeMedsFuture<-as.factor(digital_proxySG_MedicalTakeMedsFuture$MedicalTakeMedsFuture)

# number of occurance
printtable(digital_proxyUS_MedicalTakeMedsFuture$MedicalTakeMedsFuture)
printtable(digital_proxySG_MedicalTakeMedsFuture$MedicalTakeMedsFuture)

# barplot
drawbarplot(digital_proxyUS_MedicalTakeMedsFuture$MedicalTakeMedsFuture,"Bar Plot of MedicalTakeMedsFuture US","MedicalTakeMedsFuture")
drawbarplot(digital_proxySG_MedicalTakeMedsFuture$MedicalTakeMedsFuture,"Bar Plot of MedicalTakeMedsFuture SG","MedicalTakeMedsFuture")


# percentage of each categories
percentagehousing(digital_proxyUS_MedicalTakeMedsFuture$MedicalTakeMedsFuture)
percentagehousing(digital_proxySG_MedicalTakeMedsFuture$MedicalTakeMedsFuture)

```



## MedicalSeeTreatment(Poisson Distribution)

```{r}
par(mfrow = c(1,2))
FinanceAction<-as.factor(digital_proxyUS$MedicalSeeTreatment)


# number of occurance
printtable(digital_proxyUS$MedicalSeeTreatment)
printtable(digital_proxySG$MedicalSeeTreatment)

# barplot
drawbarplot(digital_proxyUS$MedicalSeeTreatment,"Bar Plot of MedicalSeeTreatment US","MedicalSeeTreatment")
drawbarplot(digital_proxySG$MedicalSeeTreatment,"Bar Plot of MedicalSeeTreatment SG","MedicalSeeTreatment")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalSeeTreatment)
percentagehousing(digital_proxySG$MedicalSeeTreatment)

```


## MedicalSeeTreatmentFuture(Multinomial Distribution)

```{r}

# helpfoodfuture
digital_proxyUS_MedicalSeeTreatmentFuture<-digital_proxyUS%>%
  select(MedicalSeeTreatment,MedicalSeeTreatmentFuture) %>%
  filter(MedicalSeeTreatment=="Never")
digital_proxySG_MedicalSeeTreatmentFuture<-digital_proxySG%>%
  select(MedicalSeeTreatment,MedicalSeeTreatmentFuture) %>%
  filter(MedicalSeeTreatment=="Never")

par(mfrow = c(1,2))
MedicalSeeTreatmentFuture<-as.factor(digital_proxyUS_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture)
MedicalSeeTreatmentFuture<-as.factor(digital_proxySG_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture)

# number of occurance
printtable(digital_proxyUS_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture)
printtable(digital_proxySG_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture)

# barplot
drawbarplot(digital_proxyUS_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture,"Bar Plot of MedicalSeeTreatmentFuture US","MedicalSeeTreatmentFuture")
drawbarplot(digital_proxySG_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture,"Bar Plot of MedicalSeeTreatmentFuture SG","MedicalSeeTreatmentFuture")


# percentage of each categories
percentagehousing(digital_proxyUS_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture)
percentagehousing(digital_proxySG_MedicalSeeTreatmentFuture$MedicalSeeTreatmentFuture)

```

## Low_Stake_Activities

```{r}
Low_Stake_Activities<-data.frame(MedicalMakeAppt=c("Daily","Weekly","Monthly","Yearly","Never"),
                                 MedicalMakeApptFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"),
                                 MedicalAccompanyAppt=c("Daily","Weekly","Monthly","Yearly","Never"),
                                 MedicalAccompanyApptFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"),
                                 MedicalTakeMeds=c("Daily","Weekly","Monthly","Yearly","Never"),
                                 MedicalTakeMedsFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"),
                                 MedicalSeeTreatment=c("Daily","Weekly","Monthly","Yearly","Never"),
                                 MedicalSeeTreatmentFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"))


Low_stake_never<-data.frame(MedicalMakeApptFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"),
                            MedicalAccompanyApptFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"),
                            MedicalTakeMedsFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"),
                            MedicalSeeTreatmentFuture=c("Very unlikely","Somewhat unlikely","Somewhat likely","Very likely","Unsure"))
```


```{r}
new_data_frame_Low_Stake_US <- digital_proxyUS[, c("MedicalMakeAppt","MedicalAccompanyAppt","MedicalTakeMeds","MedicalSeeTreatment","Low_Stake_Activities")]
head(new_data_frame_Low_Stake_US)

new_data_frame_Low_Stake_SG <- digital_proxySG[, c("MedicalMakeAppt","MedicalAccompanyAppt","MedicalTakeMeds","MedicalSeeTreatment","Low_Stake_Activities")]
head(new_data_frame_Low_Stake_SG)
```




## Medical Delegation Action (High-Stake Activities): Medical Decision Making

## MedicalDecisionPerson(Multinomial Distribution)

```{r}
print(cleaned_data4)

# number of occurance
printtable(cleaned_data3$guidance)
printtable(cleaned_data3$ongoing_assistance)
printtable(cleaned_data3$in_person_help)
printtable(cleaned_data3$unsupervised_help)
printtable(cleaned_data3$Not_Applicable)


# percentage of each categories
percentagehousing(cleaned_data3$guidance)
percentagehousing(cleaned_data3$ongoing_assistance)
percentagehousing(cleaned_data3$in_person_help)
percentagehousing(cleaned_data3$unsupervised_help)
percentagehousing(cleaned_data3$Not_Applicable)



# number of occurance
printtable(digital_proxyUS$MedicalDecisionPerson)
printtable(digital_proxySG$MedicalDecisionPerson)

# barplot
drawbarplot(digital_proxyUS$MedicalDecisionPerson,"Bar Plot of MedicalDecisionPerson US","MedicalDecisionPerson")
drawbarplot(digital_proxySG$MedicalDecisionPerson,"Bar Plot of MedicalDecisionPerson SG","MedicalDecisionPerson")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalDecisionPerson)
percentagehousing(digital_proxySG$MedicalDecisionPerson)

```


## MedicalDecisionDoctor(Multinomial Distribution)

```{r}

summary(digital_proxyUS$MedicalDecisionDoctor)

# number of occurance
printtable(digital_proxyUS$MedicalDecisionDoctor)
printtable(digital_proxySG$MedicalDecisionDoctor)

# barplot
drawbarplot(digital_proxyUS$MedicalDecisionDoctor,"Bar Plot of MedicalDecisionDoctor US","MedicalDecisionDoctor")
drawbarplot(digital_proxySG$MedicalDecisionDoctor,"Bar Plot of MedicalDecisionDoctor SG","MedicalDecisionDoctor")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalDecisionDoctor)
percentagehousing(digital_proxySG$MedicalDecisionDoctor)


```


## MedicalSignPapers(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalSignPapers)

# number of occurance
printtable(digital_proxyUS$MedicalSignPapers)
printtable(digital_proxySG$MedicalSignPapers)

# barplot
drawbarplot(digital_proxyUS$MedicalSignPapers,"Bar Plot of MedicalSignPapers US","MedicalSignPapers")
drawbarplot(digital_proxySG$MedicalSignPapers,"Bar Plot of MedicalSignPapers SG","MedicalSignPapers")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalSignPapers)
percentagehousing(digital_proxySG$MedicalSignPapers)

```



## MedicalWorthPerson(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalWorthPerson)

# number of occurance
printtable(digital_proxyUS$MedicalWorthPerson)
printtable(digital_proxySG$MedicalWorthPerson)

# barplot
drawbarplot(digital_proxyUS$MedicalWorthPerson,"Bar Plot of MedicalWorthPerson US","MedicalWorthPerson")
drawbarplot(digital_proxySG$MedicalWorthPerson,"Bar Plot of MedicalWorthPerson SG","MedicalWorthPerson")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalWorthPerson)
percentagehousing(digital_proxySG$MedicalWorthPerson)

```


## MedicalWorthDoctor(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalWorthDoctor)

# number of occurance
printtable(digital_proxyUS$MedicalWorthDoctor)
printtable(digital_proxySG$MedicalWorthDoctor)

# barplot
drawbarplot(digital_proxyUS$MedicalWorthDoctor,"Bar Plot of MedicalWorthDoctor US","MedicalWorthDoctor")
drawbarplot(digital_proxySG$MedicalWorthDoctor,"Bar Plot of MedicalWorthDoctor SG","MedicalWorthDoctor")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalWorthDoctor)
percentagehousing(digital_proxySG$MedicalWorthDoctor)


```



## MedicalWorthFamily(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalWorthFamily)

# number of occurance
printtable(digital_proxyUS$MedicalWorthFamily)
printtable(digital_proxySG$MedicalWorthFamily)

# barplot
drawbarplot(digital_proxyUS$MedicalWorthFamily,"Bar Plot of MedicalWorthFamily US","MedicalWorthFamily")
drawbarplot(digital_proxySG$MedicalWorthFamily,"Bar Plot of MedicalWorthFamily SG","MedicalWorthFamily")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalWorthFamily)
percentagehousing(digital_proxySG$MedicalWorthFamily)

```



## MedicalEndPerson(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalEndPerson)

# number of occurance
printtable(digital_proxyUS$MedicalEndPerson)
printtable(digital_proxySG$MedicalEndPerson)

# barplot
drawbarplot(digital_proxyUS$MedicalEndPerson,"Bar Plot of MedicalEndPerson US","MedicalEndPerson")
drawbarplot(digital_proxySG$MedicalEndPerson,"Bar Plot of MedicalEndPerson SG","MedicalEndPerson")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalEndPerson)
percentagehousing(digital_proxySG$MedicalEndPerson)

```


## MedicalEndDoctor(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalEndDoctor)

# number of occurance
printtable(digital_proxyUS$MedicalEndDoctor)
printtable(digital_proxySG$MedicalEndDoctor)

# barplot
drawbarplot(digital_proxyUS$MedicalEndDoctor,"Bar Plot of MedicalEndDoctor US","MedicalEndDoctor")
drawbarplot(digital_proxySG$MedicalEndDoctor,"Bar Plot of MedicalEndDoctor SG","MedicalEndDoctor")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalEndDoctor)
percentagehousing(digital_proxySG$MedicalEndDoctor)

```


## MedicalEndFamily(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalEndFamily)

# number of occurance
printtable(digital_proxyUS$MedicalEndFamily)
printtable(digital_proxySG$MedicalEndFamily)

# barplot
drawbarplot(digital_proxyUS$MedicalEndFamily,"Bar Plot of MedicalEndFamily US","MedicalEndFamily")
drawbarplot(digital_proxySG$MedicalEndFamily,"Bar Plot of MedicalEndFamily SG","MedicalEndFamily")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalEndFamily)
percentagehousing(digital_proxySG$MedicalEndFamily)


```


## MedicalFlexibilityPerson(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalFlexibilityPerson)

# number of occurance
printtable(digital_proxyUS$MedicalFlexibilityPerson)
printtable(digital_proxySG$MedicalFlexibilityPerson)

# barplot
drawbarplot(digital_proxyUS$MedicalFlexibilityPerson,"Bar Plot of MedicalFlexibilityPerson US","MedicalFlexibilityPerson")
drawbarplot(digital_proxySG$MedicalFlexibilityPerson,"Bar Plot of MedicalFlexibilityPerson SG","MedicalFlexibilityPerson")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalFlexibilityPerson)
percentagehousing(digital_proxySG$MedicalFlexibilityPerson)

```


## MedicalFlexibilityDoctor(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalFlexibilityDoctor)

# number of occurance
printtable(digital_proxyUS$MedicalFlexibilityDoctor)
printtable(digital_proxySG$MedicalFlexibilityDoctor)

# barplot
drawbarplot(digital_proxyUS$MedicalFlexibilityDoctor,"Bar Plot of MedicalFlexibilityDoctor US","MedicalFlexibilityDoctor")
drawbarplot(digital_proxySG$MedicalFlexibilityDoctor,"Bar Plot of MedicalFlexibilityDoctor SG","MedicalFlexibilityDoctor")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalFlexibilityDoctor)
percentagehousing(digital_proxySG$MedicalFlexibilityDoctor)

```


## MedicalFlexibilityFamily(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalFlexibilityFamily)

# number of occurance
printtable(digital_proxyUS$MedicalFlexibilityFamily)
printtable(digital_proxySG$MedicalFlexibilityFamily)

# barplot
drawbarplot(digital_proxyUS$MedicalFlexibilityFamily,"Bar Plot of MedicalFlexibilityFamily US","MedicalFlexibilityFamily")
drawbarplot(digital_proxySG$MedicalFlexibilityFamily,"Bar Plot of MedicalFlexibilityFamily SG","MedicalFlexibilityFamily")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalFlexibilityFamily)
percentagehousing(digital_proxySG$MedicalFlexibilityFamily)

```


## MedicalDoctorQuestions(Multinomial Distribution)

```{r}
summary(digital_proxyUS$MedicalDoctorQuestions)

# number of occurance
printtable(digital_proxyUS$MedicalDoctorQuestions)
printtable(digital_proxySG$MedicalDoctorQuestions)

# barplot
drawbarplot(digital_proxyUS$MedicalDoctorQuestions,"Bar Plot of MedicalDoctorQuestions US","MedicalDoctorQuestions")
drawbarplot(digital_proxySG$MedicalDoctorQuestions,"Bar Plot of MedicalDoctorQuestions SG","MedicalDoctorQuestions")

# percentage of each categories
percentagehousing(digital_proxyUS$MedicalDoctorQuestions)
percentagehousing(digital_proxySG$MedicalDoctorQuestions)

```


## Digital Caregiver Account and Number (Multinomial Distribution)

```{r}
digital_proxyUS_caregiveraccount<-digital_proxyUS%>%
  select(DigitalCaregiverAccount,DigitalCaregiverAccountNum) %>%
  filter(DigitalCaregiverAccount=="Yes")
digital_proxySG_caregiveraccount<-digital_proxySG%>%
  select(DigitalCaregiverAccount,DigitalCaregiverAccountNum) %>%
  filter(DigitalCaregiverAccount=="Yes")

DigitalCaregiverAccount<-as.factor(digital_proxyUS$DigitalCaregiverAccount)
DigitalCaregiverAccountNum<-as.factor(digital_proxyUS_caregiveraccount$DigitalCaregiverAccountNum)

# number of occurance
printtable(digital_proxyUS$DigitalCaregiverAccount)
printtable(digital_proxyUS$DigitalCaregiverAccount)

printtable(digital_proxyUS_caregiveraccount$DigitalCaregiverAccountNum)
printtable(digital_proxySG_caregiveraccount$DigitalCaregiverAccountNum)

# barplot
drawbarplot(digital_proxyUS$DigitalCaregiverAccount,"Bar Plot of DigitalCaregiverAccount US","DigitalCaregiverAccount")
drawbarplot(digital_proxyUS$DigitalCaregiverAccount,"Bar Plot of DigitalCaregiverAccount SG","DigitalCaregiverAccount")

drawbarplot(digital_proxyUS_caregiveraccount$DigitalCaregiverAccountNum,"Bar Plot of DigitalCaregiverAccountNum US","DigitalCaregiverAccountNum")
drawbarplot(digital_proxySG_caregiveraccount$DigitalCaregiverAccountNum,"Bar Plot of DigitalCaregiverAccountNum SG","DigitalCaregiverAccountNum")

# percentage of each categories
percentagehousing(digital_proxyUS$DigitalCaregiverAccount)
percentagehousing(digital_proxyUS$DigitalCaregiverAccount)

percentagehousing(digital_proxyUS_caregiveraccount$DigitalCaregiverAccountNum)
percentagehousing(digital_proxySG_caregiveraccount$DigitalCaregiverAccountNum)

```



### whether low-stake Activities will influence the High-stake Activities? (What variables will influence low-stake Activities, such as ADL, IADL)


## High_Stake_Activities

```{r}
High_Stake_Activities<-data.frame(MedicalDecisionPerson=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalDecisionDoctor=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalSignPapers=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalWorthPerson=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalWorthDoctor=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalWorthFamily=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalEndPerson=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalEndDoctor=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalEndFamily=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalFlexibilityPerson=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalFlexibilityDoctor=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalFlexibilityFamily=c("Yes","No, but I should have","No, because I didn't need to"),
                                 MedicalDoctorQuestions=c("Yes","No, but I should have","No, because I didn't need to"),
                                 DigitalCaregiverAccount=c("Yes","No, but I should have","No, because I didn't need to"))
```



## DigitalAssistMedical(Binomial Distribution)

```{r}
par(mfrow = c(1,2))
DigitalAssistMedical<-as.factor(digital_proxyUS$DigitalAssistMedical)

# number of occurance
printtable(digital_proxyUS$DigitalAssistMedical)
printtable(digital_proxySG$DigitalAssistMedical)

# barplot
drawbarplot(digital_proxyUS$DigitalAssistMedical,"Bar Plot of DigitalAssistMedical US","DigitalAssistMedical")
drawbarplot(digital_proxySG$DigitalAssistMedical,"Bar Plot of DigitalAssistMedical SG","DigitalAssistMedical")

# percentage of each categories
percentagehousing(digital_proxyUS$DigitalAssistMedical)
percentagehousing(digital_proxySG$DigitalAssistMedical)

```


## DigitalAssistReasons(Multinomial Distribution)

```{r}
print(cleaned_data4)
par(mfrow = c(2,2))

# number of occurance
printtable(cleaned_data4$not_user_friendly)
printtable(cleaned_data4$difficult)
printtable(cleaned_data4$concerns_data)
printtable(cleaned_data4$unfamiliar)
printtable(cleaned_data4$physical_limitations)
printtable(cleaned_data4$cognitive_limiation)
printtable(cleaned_data4$no_device)
printtable(cleaned_data4$Others)


# percentage of each categories
percentagehousing(cleaned_data4$not_user_friendly)
percentagehousing(cleaned_data4$difficult)
percentagehousing(cleaned_data4$concerns_data)
percentagehousing(cleaned_data4$unfamiliar)
percentagehousing(cleaned_data4$physical_limitations)
percentagehousing(cleaned_data4$cognitive_limiation)
percentagehousing(cleaned_data4$no_device)
percentagehousing(cleaned_data4$Others)

```


## DigitalAssistAccessWays(Multinomial Distribution)

```{r}
print(cleaned_data5)

# number of occurance
printtable(cleaned_data5$username_password)
printtable(cleaned_data5$fingerprint)
printtable(cleaned_data5$donot_know)
printtable(cleaned_data5$proxy_account)


# percentage of each categories
percentagehousing(cleaned_data5$username_password)
percentagehousing(cleaned_data5$fingerprint)
percentagehousing(cleaned_data5$donot_know)
percentagehousing(cleaned_data5$proxy_account)

```


## DigitalAssistUseWays(Multinomial Distribution)

```{r}
print(cleaned_data6)

# number of occurance
printtable(cleaned_data6$guidance)
printtable(cleaned_data6$ongoing_assistance)
printtable(cleaned_data6$in_person_help)
printtable(cleaned_data6$unsupervised_help)
printtable(cleaned_data6$Not_Applicable)


# percentage of each categories
percentagehousing(cleaned_data6$guidance)
percentagehousing(cleaned_data6$ongoing_assistance)
percentagehousing(cleaned_data6$in_person_help)
percentagehousing(cleaned_data6$unsupervised_help)
percentagehousing(cleaned_data6$Not_Applicable)

```



```{r}
new_data_frame_High_Stake_US <- digital_proxyUS[, c("MedicalDecisionPerson","MedicalDecisionDoctor","MedicalSignPapers","MedicalWorthPerson","MedicalWorthDoctor","MedicalWorthFamily","MedicalEndPerson","MedicalEndDoctor","MedicalEndFamily","MedicalFlexibilityPerson","MedicalFlexibilityDoctor","MedicalFlexibilityFamily","MedicalDoctorQuestions","DigitalCaregiverAccount","High_Stake_Activities")]
head(new_data_frame_High_Stake_US)

new_data_frame_High_Stake_SG <- digital_proxySG[, c("MedicalDecisionPerson","MedicalDecisionDoctor","MedicalSignPapers","MedicalWorthPerson","MedicalWorthDoctor","MedicalWorthFamily","MedicalEndPerson","MedicalEndDoctor","MedicalEndFamily","MedicalFlexibilityPerson","MedicalFlexibilityDoctor","MedicalFlexibilityFamily","MedicalDoctorQuestions","DigitalCaregiverAccount","High_Stake_Activities")]
head(new_data_frame_High_Stake_SG)
```





